The first prediction of Black hole mass function and its evolution by ET

### 2019-05-08 GW_BH_function/manuscript_GW_constrain_BHmass/main.tex
finish paper draft on my side

\title{Black hole mass function and redshift evolution by ET}

@@

\author%[0000-0001-8917-2148]
{Xuheng Ding}
\affiliation{School of Physics and Technology, Wuhan University, Wuhan 430072, China}
\affiliation{Department of Physics and Astronomy, University of California, Los Angeles, CA, 90095-
1547, USA}

\author{Lilan Yang}
\affiliation{School of Physics and Technology, Wuhan University, Wuhan 430072, China}
\affiliation{Department of Physics and Astronomy, University of California, Los Angeles, CA, 90095-
1547, USA}

@@

\author%[0000-0002-4359-5994]
{Kai Liao}
\affiliation{School of Science, Wuhan University of Technology, Wuhan 430070, China}

@@

\begin{abstract}
%discover of GW
%Measure of BH mass and thus fit the BH mass.
%The discovery of double compact objects by GW provide a the measurement of their BH masses. Recent works by LIGO group have constrained 10 GW event and constrain the BHs. The ET would detect more GW events with DL and BH mass up to redshift $z\sim10$, and thus enable one to constrain the mass function and study how it evolution with redshift. In this work, test the ability of 1000 GWs events by ET. We tested, 1. how well are they able to recover the BH mass function as power law distribution. 2. If the GW events are able to tell a redshifted-related BH mass function.
We demonstrate the ability of future gravitational-wave (GW) measured by third generation detector Einstein telescope (ET) to infer the slope of the BH mass function (BHMF) and its evolution with redshift. %The measurement of BH binary systems enable the inference of the BH mass (\mone\ and \mtwo\ of each component) together with the luminosity distance (\dl).
We performed Monte Carlo approach to simulate the measurements of BH binaries GW signals as detected by ET, including the BH masses and their luminosity distance (\dl). Following the recent works by Kovetz et al. (2017) and LIGO-Virgo (2018), we consider the more massive black hole in each binary and model the BHMF as a function of power law with slope parameter as $\alpha$. We find that only a thousand GW events ($\sim1\%$ amount of the yearly detection rate) could measure the $\alpha$ to $3\%$ accuracy level. Furthermore, we investigate a scenario that  $\alpha$ is evolving with redshift. We find that using the \dl\ as redshift estimator, one is able to distinguish the evolution trend between positive and negative. This may help to understand the origin of the BHs and how BH binaries formed at different stage of the Universe.

@@

\section{Introduction} \label{sec_intro}
As first identified as a solution to Einstein's field equations by Schwarzschild in 1916, black holes (BHs) have been predicted to remain a bunches of fundamental questions in unifying GR with quantum physics (Hawking 1976; Giddings 2017). The mass of BHs is known to cover a wide range from stellar-mass to supermassive ($\sim10^{10} M_{\odot}$). The recent discovery of gravitational-wave (GW) measurement is a substantial evidence of stellar-mass BHs (Abbott et al. 2016), while supermassive BHs are thought to be existed in the centers of most all the galaxies. More recently, the first image of supermassive BH in the center of the giant elliptical galaxy M87 has been reconstructed by radio-wave observations. Nevertheless, in theory, it is still unclear of how the BHs are formed. The prediction for the number and mass distribution of stellar-mass BHs is still in the Universe is needed to be more clear.

The recent detections by LIGO bring us to a new era of GW astronomy. \textcolor{blue}{COPY THE INTRODUCE THE RECENT LIGO RESULT: Overall, advanced LIGO in its 2015 O1 run observed three1 BH coalescence events, adding nine additional measured black hole masses to the current data (the six premerger masses range from roughly 7 to 36 Mstar). Over the next decade, improvements in detector sensitivities are expected to usher in a wave of newly detected events. LIGO itself is scheduled to perform two more runs (O2,3) with increasing sensitivity before commencing a multiyear run at its design sensitivity at the turn of the decade.} 
The GWs provide a direct way to hear the inspiralling binary BH (BBH) systems, enable one to derive their information including mass, spin, luminosity distance.
This bring us the opportunity to measure the population of BHs and help to answer some fundamental questions such as the cosmography, the GW speed. the strong lensing effects. 
%The detection of GWs are able one to measure the BH mass thus understand the BH mass function. Introducing the importance of BH mass function.

More recently, the LIGO collaboration has used ten BBH merger events and constrained the BHMF as power law index to $\alpha~=~1.6\substack{+1.5\\-1.7}$ (90\% credibility). The previous work (Kovetz 2017) has investigated that further LIGO measurements from thousands of BBHs can be taken to infer the power law index $\alpha$ at 10\% accuracy. In this study, we pay extra attentions on simulating the GW events that could be measured by ET based Monte Carlo (MC) approach. This provides us a BBHs catalog with realistic dataset to exam their ability to constrain the BHMFs, putting the data noise level, selection effects in a more realistic way. Moreover, the ET would detect the GW event at distant Universe up to $z\sim17$; we take the luminosity distance as the redshift estimator and exam whether one could detect the $\alpha$ as a function of redshift.

This paper is organized as follows. In Sec~\ref{sec_simulation} we describe the simulation of the BBHs events that detected by ET using MC approach. In this section, we adopt our initial assumptions for the BH mass function as the truth. In Sec~\ref{sec_theory}, we introduce the theoretical framework as used to reconstruct the BHMFs, including the noise realization and the selection effects. Furthermore, we make a further step by considering the power law index $\alpha$ as a function of redshift and explore the way to use luminosity distance as redshift estimator and detect such evolution. We present our results in the Section. The discussion and conclusions are given in the final Section.

@@

\section{Data simulation} \label{sec_simulation}
%\subsection{The simulation of GW events and the detection by ET} \label{subsec_BHMF_redshift}
%Rather than numerical calculation, we use Monto Carlo to simulate the GW signal.
%1. We randomly generate the DCOs with redshift number density as the Dominique's startrack.
%2. We consider for each event,  we randomly assuming its properties, including  $\Theta$, with BH mass as power law.
%3. Knowing the DL, $\Theta$, $\cal M$, we are able to simulation their $\rho$ and test whether could be detected by ET.
%4. Add noise level. We assuming the Dl, $\cal M$, $m_1$, $m_2$ as lognormal distribution.
%\begin{itemize}
%%\renewcommand\labelitemi{--}
%\item We randomly generate the DCOs with redshift number density as the Dominique's startrack.
%\item We consider for each event,  we randomly assuming its properties, including  $\Theta$, with BH mass as power law.
%\item Knowing the DL, $\Theta$, $\cal M$, we are able to simulation their $\rho$ and test whether could be detected by ET.
%\item Add noise level. We assuming the Dl, $\cal M$, $m_1$, $m_2$ as lognormal distribution.
%\end{itemize}
We simulate the GW signal of BBHs that would be obtained in the future ET detection in this section. The nurmecial predictions of the events heard by ET have been discussed in many works, and forecasted that the yearly detection rate of BBHs would be $\sim10^{4-5}.$ More recently, Yang et al. (2019) developed the MC approach to predict the detection rate by explicitly considering each BBHs event, which provides the way to mimic a realistic BBH GW catalog for us to test. The backbone is to build up a mock universe which includes a sufficient volume of BBH events to represent the overall.  We refer the reader for the details in Yang et al. (section 2, 2019) and briefly recall the key points here.

\subsection{Detection Criteria} \label{subsec_criteria}
The values of the key parameters that determined the GW signal-to-noise ratio (\snr) are randomly generated. For a specific BBG event at redshift $z_s$, the ET's reaction of this event is:

\begin{equation} \label{SNR}
\rho = 8 \Theta \frac{r_0}{d_L(z_s)} \left( \frac{(1+z){\cal M}_0}{1.2 M_{\odot}} \right)^{5/6}
\sqrt {\zeta(f_{max})},
\end{equation}
where $r_0$ is the detector's characteristic distance parameter and $\zeta(f_{max})$ is the dimensionless function reflecting the overlap between the GW signal and the ET's effective bandwidth which is usually simplified as unity. ${\cal M}_0$ is the intrinsic chirp mass which is calculated as $ {\cal M}_0 = \frac{(m_1m_2)^{3/5}}{(m_1+m_2)^{1/5}}$, where the \mone\ and \mtwo\ are the each BH mass in the binary. $\Theta$ is the orientation factor determined by four angles as:
 \begin{equation} \label{Theta}
 \Theta = 2 [ F_{+}^2(1 + \cos^2{\iota} )^2 + 4 F_{\times}^2 \cos^2{\iota} ]^{1/2},
 \end{equation}
where: $F_{+} = \frac{1}{2} (1 + \cos^2{\theta}) \cos{2\phi} \cos{2 \psi} - \cos{\theta} \sin{2 \phi} \sin{ 2 \psi}$, and
$F_{\times} = \frac{1}{2} (1 + \cos^2{\theta}) \sin{2\phi} \cos{2 \psi} + \cos{\theta} \sin{2 \phi} \cos{ 2 \psi}$ are so-called antenna patterns. The four angles ($\theta, \phi, \psi, \iota$) are independent, with $(\cos\theta, \phi/\pi, \psi/\pi, \cos\iota)$ distributed uniformly over the range $[-1, 1]$.

The GW signals are considered as detectable if their \snr\ are over the detecting threshold, i.e., $\rho > \rho_0 = 8$.

\subsection{Monte Carlo Approach} \label{MC}
We build up a sufficient volume of BBHs systems in the mock universe, and randomly generate the key parameters for each BBH systems. To build up this volume, we follow previous steps by adopting the intrinsic BBH merger rates $\dot{n}_{0}(z_{s})$ predicted by the population synthesis model (using {\tt StarTrack} code\footnote{The data is taken from the website \url{http://www.syntheticuniverse.org}.}) in Dominik et al. (2013). Therefore, the yearly  merging rate of BBH sources in a redshift interval  $[z_{s}, z_{s}+dz_{s}]$ is 
 \begin{equation}
 d\dot{N} (z_s)=4\pi\left(\frac{c}{H_{0}}\right)^3\frac{\dot{n}_{0}(z_{s})}{1+z_{s}}\frac{\tilde{r}^2(z_{s})}{E(z_{s})}dz_{s}. 
 \end{equation}
Hence, the overall BBHs in the universe can be calculated as ${\dot N} = \int_0^{ \infty} \frac{d {\dot N (z)}}{dz} dz$.

For each BBH systems, we following the possibility distribution of the key parameters to randomly generate their values. The key parameters includes the four angles (i.e., $\theta, \phi, \psi, \iota$, see the Equation~\ref{Theta} and its description) and the each BH mass in the binary systems (i.e., \mone\ and \mtwo).

To randomly simulate the BH masses, we follow the previous works by LIGO 2019 and assuming the BHMF of the more massive BH mass, \mone, following a power law distribution as:
 \begin{equation} \label{equ_powlaw}
p(m_1|\alpha, M_{max}, M_{min}) = m_1^{\alpha} \mathcal{H}(m_1-M_{min}) \mathcal{H}(M_{max}-m_1),
 \end{equation}
where $\mathcal{H}$ is the Heaviside step function. Then, the secondary mass, \mtwo, is fix as uniform between $[M_{min}, m_1]$. Note that, in the next section, we only take the \mone\ to reconstruct the BHMF, thus the assumption of the distribution for \mtwo\ would not affect our inference for the shape of BHMF.

The generation of these parameters would determine the value of $\Theta$ and ${\cal M}_0$. We combine them with their redshift to realize the $\rho$ of each BBH system.
We aim to collect the events which have $\rho > \rho_0 = 8$ so as to estimate the yearly detection rate.

In this paper, we consider the BHMF as two scenarios. In the first scenario, the $\alpha$ is a constant value and we adopt the values $\alpha~=~2.35$, $M_{min}~=~5M_{\odot}$, $M_{max}~=~80M_{\odot}$ as our fiducial model. In the second scenario, we consider that $\alpha$ varies as a function of redshift in formalism as:
 \begin{equation} \label{equ_alphaz}
\alpha(z) = \alpha_0 + \alpha_1\frac{z}{1+z} , 
 \end{equation}

so that the $\alpha(z)$ would transform gradually from $\alpha_0$ to $\alpha_0+\alpha_1$ through low$-z$ to high$-z$. We adopt the values $\alpha_0~=~2.35$, $\alpha_1~=~0.75$, $M_{min}~=~5M_{\odot}$, $M_{max}~=~80M_{\odot}$ as the truth.

\subsection{Measurement Error} \label{sec_noiselevel}
Our simulation provides a mock dataset of the future GW events as measured by ET. To consider the measurements in a realistic way, we take the random statistical errors into account here.

We assume the observed probability distribution with their uncertainty level of the data, including the \mone, \mtwo, and \dl. In theory, the \mone\ and \mtwo\ are constrained from the combining of the chirp mass (a direct measurement by the inspiral) and the total mass (i.e., \mone+\mtwo, which is more sensitive to the ringdown waveform).

In Archisman et al. (2015), the expected statistical errors of the measurement has been estimated with Bayesian parameter estimation. We adopt their implications as our guidance to setup noise level of our simulated data.  Nevertheless, we note that the measurements of the GW are ${\it skewed}$. Other than the traditional Gaussian distribution, we assume the properties of the measurements follow the Log-Normal distribution (i.e. their $log$ value follows the Gaussian). As a consequence, we assume the standard deviation of \mone\ \dl, and ${\cal M}_0$ as 0.2, 0.35 and 0.17, respectively. For instance, if the $m_{1,fid}$ is the true value for \mone, its possibility distribution of measured value follows:
 \begin{equation} \label{equ_lognorm}
p(m) = \frac{1}{m\sigma\sqrt{2\pi}} exp \big(- \frac{log(m)-log(m_{1,fid})}{2\sigma} \big) 
 \end{equation}

As a demonstration, we list a thousand-like simulated data in Table~\ref{tab_GW_mock_data}, which we would take to infer the BHMFs in one realization.

>>>>

\title{The first prediction of Black hole mass function and its evolution by ET}

@@

\author%[0000-0001-8917-2148]
{Xuheng Ding}
\affiliation{School of Physics and Technology, Wuhan University, Wuhan 430072, China}
\affiliation{Department of Physics and Astronomy, University of California, Los Angeles, CA, 90095-1547, USA}

%\author{Lilan Yang}
%\affiliation{School of Physics and Technology, Wuhan University, Wuhan 430072, China}
%\affiliation{Department of Physics and Astronomy, University of California, Los Angeles, CA, 90095-1547, USA}

@@

%\author%[0000-0002-4359-5994]
%{Kai Liao}
%\affiliation{School of Science, Wuhan University of Technology, Wuhan 430070, China}

@@

\begin{abstract}
%discover of GW
%Measure of BH mass and thus fit the BH mass.
%The discovery of double compact objects by GW provide a the measurement of their BH masses. Recent works by LIGO group have constrained 10 GW event and constrain the BHs. The ET would detect more GW events with DL and BH mass up to redshift $z\sim10$, and thus enable one to constrain the mass function and study how it evolution with redshift. In this work, test the ability of 1000 GWs events by ET. We tested, 1. how well are they able to recover the BH mass function as power law distribution. 2. If the GW events are able to tell a redshifted-related BH mass function.
We demonstrate the ability of future gravitational-wave (GW) measured by third generation detector Einstein Telescope (ET) to infer the slope of the BH mass function (BHMF) and its evolution with redshift. %The measurement of BH binary systems enable the inference of the BH mass (\mone\ and \mtwo\ of each component) together with the luminosity distance (\dl).
We performed the Monte Carlo approach to simulate the measurements of BH binaries GW signals as detected by ET, including the BH masses and their luminosity distance (\dl). Following the previous works, we consider the mass of  primary black hole in each binary and model the BHMF as a function of the power law with slope parameter as $\alpha$. We take into account the bias that would be raised by the uncertainty of the measurement and the selection effect and find that a thousand GW events measure by ET ($\sim1\%$ amount of the yearly detection rate) could measure the $\alpha$ to $3\%$ accuracy level. Furthermore, we investigate a scenario, by the first time, that  $\alpha$ is evolving with redshift as $\alpha(z) = \alpha_0 + \alpha_1\frac{z}{1+z}$. Our result is that, taking the \dl\ as redshift estimator, with a thousand GW events one is capable of obtaining an unbiased $\alpha_1$ at the uncertainty level of $\pm0.5$. The ability of known the evolution scenario of BHMF would help to understand the origin of the BHs and how BH binaries formed at the different stage of the Universe.

@@

\section{Introduction} \label{sec_intro}
As first identified as a solution to Einstein's field equations by Schwarzschild in 1916 \citep{Schwarzschild1999}, black holes (BHs) have been predicted to remain a bunches of fundamental questions in unifying GR with quantum physics \citep{Hawking1976, Giddings2017}. The mass of BHs is known to cover a wide range from stellar-mass to supermassive ($\sim10^{10} M_{\odot}$). The recent discovery of gravitational-wave (GW) measurement is a substantial evidence of stellar-mass BHs \citep{Abbott2016}, while supermassive BHs are thought to existe in the centers of almost all the galaxies \citep{Lynden-Bell1969, Kormendy1995}. More recently, the first image of supermassive BH in the center of the giant elliptical galaxy M87 has been reconstructed by radio-wave observations \citep{Alberdi2019}. Nevertheless, in theory, it is still unclear of how the BHs are formed \citep{Fryer1999, Fryer2001, Mirabel2016}. The prediction for the number and mass distribution of stellar-mass BHs in the Universe is still needed to be more clear.

The recent GW detection activities have brought us to a new era of GW astronomy \citep[e.g.,][]{Abbott2016, Abbott2016_sum, Abbott2018}. To date, the LIGO and Virgo have achieved two successful runs (O1 and O2) and now is performing the third run (O3). In the first run O1 (from September 12th, 2015 to January 19th, 2016), the first catalog of binary BH (BBH) inspiral systems have been measured including three BBH systems. In the O2 run (from November 30th, 2016 to August 25th, 2017), a total of seven binary black hole mergers have been detected\footnote{Together with the first detection of GW from detection of binary neutron star inspiral system.}. In the next decade, the volume of the events is expected to be increasing rapidly with the improvements in the detector sensitivities.

The GWs provide a direct way to hear the inspiralling BBH systems, enable one to derive their information including mass, spin, luminosity distance\citep{Abbott2017phy}. This brings us the opportunity to measure the population of BHs \citep{Abbott2018b} and helps to answer some fundamental questions such as the cosmography\citep{Liao2017, Ding2019, Cai2017}, the GW speed\citep{Fan2017, Collett2017}, the strong lensing effects~\citep{Ola2013, Biesiada2014, Ding2015}. 
The previous work \citet{Kovetz2017PhRvD} has investigated that further LIGO measurements from thousands of BBHs can be taken to infer the power law index $\alpha$ at 10\% accuracy. More recently, the LIGO collaboration has used ten BBH merger events and constrained the BHMF as power law index to $\alpha~=~1.6\substack{+1.5\\-1.7}$ (90\% credibility) \citep{Abbott2018b}. In this study, we pay extra attention on simulating the GW events that could be measured by third-generation gravitational waves detector, Einstein Telescope (ET) \citep{Abernathy2011} based Monte Carlo (MC) approach. This provides us a mock BBHs catalog with the realistic dataset to exam their ability to constrain the BHMFs, taking into the effects by the data noise level, selection bias in a more realistic way. Moreover, the ET would detect the GW event at distant Universe up to $z\sim17$ \citep{Abernathy2011}. The wide redshift range of the events enable us to exam whether it is possible to detect the $\alpha$ as a function of redshift.

This paper is organized as follows. In Sec~\ref{sec_simulation} we describe the simulation of the BBHs events that detected by ET using the Monte Carlo approach. In this section, we assume the initial assumptions for the BH mass function as the truth. In Sec~\ref{sec_theory}, we introduce the theoretical framework to reconstruct the BHMFs, considering the noise realization and the selection effects. Furthermore, we make a further step by considering the power law index $\alpha$ as a function of redshift and explore the way to use luminosity distance as redshift estimator and detect such evolution. We present our results in the Section~\ref{sec_result}. The discussion and conclusions are given in the last Section~\ref{sec_summary}.

@@

\vspace{1cm}
\section{Data simulation} \label{sec_simulation}
%\subsection{The simulation of GW events and the detection by ET} \label{subsec_BHMF_redshift}
%Rather than numerical calculation, we use Monto Carlo to simulate the GW signal.
%1. We randomly generate the DCOs with redshift number density as the Dominique's startrack.
%2. We consider for each event,  we randomly assuming its properties, including  $\Theta$, with BH mass as power law.
%3. Knowing the DL, $\Theta$, $\cal M$, we are able to simulation their $\rho$ and test whether could be detected by ET.
%4. Add noise level. We assuming the Dl, $\cal M$, $m_1$, $m_2$ as lognormal distribution.
%\begin{itemize}
%%\renewcommand\labelitemi{--}
%\item We randomly generate the DCOs with redshift number density as the Dominique's startrack.
%\item We consider for each event,  we randomly assuming its properties, including  $\Theta$, with BH mass as power law.
%\item Knowing the DL, $\Theta$, $\cal M$, we are able to simulation their $\rho$ and test whether could be detected by ET.
%\item Add noise level. We assuming the Dl, $\cal M$, $m_1$, $m_2$ as lognormal distribution.
%\end{itemize}
We simulate the GW signal of BBHs that would be obtained in the future ET detection in this section. The numerical predictions of the events heard by ET have been discussed in many works, and forecasted that the yearly detection rate of BBHs would be $\sim10^{4-5}$ \citep{Abernathy2011, Ola2013, Biesiada2014}. More recently, \citet{Yang2019} developed the approach the Monte Carlo (MC) simulation to predict the detection rate by explicitly considering each BBHs event, which provides the way to mimic a realistic BBH GW catalog. The backbone is to build up a mock universe which includes a sufficient volume of BBH events to represent the overall sample. We refer the reader for the details in \citet[][Section 2, therein]{Yang2019}  and briefly recall the key points here.

\subsection{Detection Criteria} \label{subsec_criteria}
We randomly generated the key parameters to determine the intensity (i.e., signal-to-noise ratio, SNR) of each GW system. For a specific BBH event at redshift $z_s$, the ET's corresponding reaction is defined as \citep{Abernathy2011}:

\begin{equation} \label{SNR}
\rho = 8 \Theta \frac{r_0}{d_L(z_s)} \left( \frac{(1+z){\cal M}_0}{1.2 M_{\odot}} \right)^{5/6}
\sqrt {\zeta(f_{max})},
\end{equation}
where $r_0$ is the detector's characteristic distance parameter and $\zeta(f_{max})$ is the dimensionless function reflecting the overlap between the GW signal and the ET's effective bandwidth which is usually simplified as unity. ${\cal M}_0$ is the intrinsic chirp mass which is calculated as $ {\cal M}_0 = \frac{(m_1m_2)^{3/5}}{(m_1+m_2)^{1/5}}$, where the \mone\ and \mtwo\ are the each BH mass in the binary. $\Theta$ is the orientation factor determined by four angles as \citep{Finn93}:
 \begin{equation} \label{Theta}
 \Theta = 2 [ F_{+}^2(1 + \cos^2{\iota} )^2 + 4 F_{\times}^2 \cos^2{\iota} ]^{1/2},
 \end{equation}
where: $F_{+} = \frac{1}{2} (1 + \cos^2{\theta}) \cos{2\phi} \cos{2 \psi} - \cos{\theta} \sin{2 \phi} \sin{ 2 \psi}$, and
$F_{\times} = \frac{1}{2} (1 + \cos^2{\theta}) \sin{2\phi} \cos{2 \psi} + \cos{\theta} \sin{2 \phi} \cos{ 2 \psi}$ are so-called antenna patterns. The four angles ($\theta, \phi, \psi, \iota$) are independent, with $(\cos\theta, \phi/\pi, \psi/\pi, \cos\iota)$ distributed uniformly over the range $[-1, 1]$. Note that the GW signals are considered as detectable if their \snr\ are over the detecting threshold, i.e., $\rho > \rho_0 = 8$.

\subsection{Monte Carlo Approach} \label{MC}
We build up a sufficient volume of BBHs systems in the mock universe, and randomly generate the key parameters for each BBH systems. To build up this volume, we follow previous steps by adopting the intrinsic BBH merger rates $\dot{n}_{0}(z_{s})$ predicted by the population synthesis model (using {\tt StarTrack} code\footnote{The data is taken from the website \url{http://www.syntheticuniverse.org}.}) in \citet{Dominik13}. Therefore, the yearly  merging rate of BBH sources in a redshift interval  $[z_{s}, z_{s}+dz_{s}]$ is 
 \begin{equation}
 d\dot{N} (z_s)=4\pi\left(\frac{c}{H_{0}}\right)^3\frac{\dot{n}_{0}(z_{s})}{1+z_{s}}\frac{\tilde{r}^2(z_{s})}{E(z_{s})}dz_{s}. 
 \end{equation}
Hence, the overall amount of BBH events in the universe can be calculated by ${\dot N} = \int_0^{ \infty} \frac{d {\dot N (z)}}{dz} dz$.

For each BBH systems, we following the possibility distribution of the key parameters to randomly generate their values. These key parameters include the four angles (i.e., $\theta, \phi, \psi, \iota$ in Equation~\ref{Theta}) and the masses of each BHs in the binary systems (i.e., \mone\ and \mtwo).

To randomly generate the BH masses, we follow the previous works \citep{Kovetz2017PhRvD, Abbott2018b, Fishbach2018} and assume the \mone\ follows a power law distribution with hard cut at both maximum and minimum mass:
 \begin{equation} \label{equ_powlaw}
p(m_1|\alpha, M_{max}, M_{min}) = m_1^{\alpha} \mathcal{H}(m_1-M_{min}) \mathcal{H}(M_{max}-m_1),
 \end{equation}
where $\mathcal{H}$ is the Heaviside step function. Then, the secondary mass, \mtwo, is fix as uniform between $[M_{min}, m_1]$. Note that, we only take the \mone\ to reconstruct the BHMF, thus the assumption of the distribution for \mtwo\ actually does not affect the inference for the shape of BHMF.
The generation of these parameters would determine the value of $\Theta$ and ${\cal M}_0$ in Equation~\ref{SNR}. We combine them with their redshift to realize the $\rho$ of each BBH system. We collect the events which have $\rho > \rho_0 = 8$, meaning that those events with $\rho < 8$ are to faint to be detected.

We consider the BHMF contains two scenarios. In the first scenario, the $\alpha$ is a constant value and the shape of the BHMF is fix throughout the redshfit. In the second scenario, we consider that $\alpha$ varies as a function of redshift in formalism as:
 \begin{equation} \label{equ_alphaz}
\alpha(z) = \alpha_0 + \alpha_1\frac{z}{1+z} , 
 \end{equation}
so that the $\alpha(z)$ would transform gradually from $\alpha_0$ to $\alpha_0+\alpha_1$ through low$-z$ to high$-z$.

\subsection{Measurement Error} \label{sec_noiselevel}
We aim to produce the mock dataset of the future GW events as measured by ET. To consider the measurement error in a realistic way, we inject the random statistical errors into the mock data in this section.

The measurement of the BBH inspiral parameters including the \dl, chirp mass, m1, m2, and SNR. In practice, the \mone\ and \mtwo\ are derived from the combination of the chirp mass and the total mass (i.e., \mone+\mtwo, which is more sensitive to the ringdown waveform). We adopt the implications by \citet{Ghosh2016}, which explore the statistical errors of the measurement with Bayesian parameter estimation, as our recipe to set up the noise level of our simulated data.  In addition, we note that the measurements of the GW are ${\it skewed}$. Other than the traditional Gaussian distribution, we assume the properties of the measurements follow the Log-Normal distribution (i.e. their $log$ value follows the Gaussian) with the standard deviation as 0.2, 0.35 and 0.17 for \mone\ \dl, and ${\cal M}_0$, respectively. For instance, if the $m_{1,fid}$ is the true value for \mone, its possibility distribution of measured value follows:
 \begin{equation} \label{equ_lognorm}
p(m) = \frac{1}{m\sigma\sqrt{2\pi}} exp \big(- \frac{log(m)-log(m_{1,fid})}{2\sigma} \big) 
 \end{equation}

Having clarified the MC approach and defined data the uncertainty level, we are capable of producing the mock GW dataset. As a demonstration, we list a thousand-like simulated data in Table~\ref{tab_GW_mock_data}, which we would take to infer the BHMFs in per realization.

\begin{deluxetable}{lcccc}
\tablecolumns{5}
\tabletypesize{\footnotesize}
\tablewidth{0pt}
\tablecaption{Demonstration of the mock GW catalog} 
\tablehead{ 
\colhead{Object ID} &
\colhead{\mone}&
\colhead{Luminosity Distance} & 
\colhead{Chirp Mass} &
\colhead{SNR}
\\ 
\colhead{} &
\colhead{($M_\odot$)}&
\colhead{(Mpc)} & 
\colhead{($M_\odot$)} &
\colhead{(\snr)}
\\
\colhead{(1)} &
\colhead{(2)} &
\colhead{(3)} &
\colhead{(4)} &
\colhead{(5)}
} 
\startdata
%\multicolumn{5}{c}{Sample presented in \citet{Treu+07}}\\
%\\
ID1 & $95.85\substack{+21.22\\-17.37}$  & $87120.7\substack{+19288.8\\-15792.3}$  & $61.87\substack{+13.70\\-11.21}$ & 28.707 \\
ID2 & $13.31\substack{+2.95\\-2.41}$  & $81476.5\substack{+18039.1\\-14769.2}$  & $11.68\substack{+2.59\\-2.12}$ & 10.468 \\
ID3 & $7.40\substack{+1.64\\-1.34}$  & $7456.8\substack{+1651.0\\-1351.7}$  & $6.82\substack{+1.51\\-1.24}$ & 39.673 \\
ID4 & $19.02\substack{+4.21\\-3.45}$  & $96201.9\substack{+21299.4\\-17438.4}$  & $19.11\substack{+4.23\\-3.46}$ & 12.227 \\
ID5 & $15.12\substack{+3.35\\-2.74}$  & $47645.3\substack{+10548.8\\-8636.6}$  & $14.24\substack{+3.15\\-2.58}$ & 12.672 \\
ID6 & $18.95\substack{+4.20\\-3.43}$  & $23937.4\substack{+5299.8\\-4339.1}$  & $13.86\substack{+3.07\\-2.51}$ & 16.027 \\
ID7 & $8.65\substack{+1.92\\-1.57}$  & $44053.0\substack{+9753.4\\-7985.4}$  & $6.99\substack{+1.55\\-1.27}$ & 8.383 \\
ID8 & $40.03\substack{+8.86\\-7.26}$  & $60432.5\substack{+13379.9\\-10954.6}$  & $25.53\substack{+5.65\\-4.63}$ & 17.917 \\
ID9 & $32.58\substack{+7.21\\-5.91}$  & $4293.5\substack{+950.6\\-778.3}$  & $18.58\substack{+4.11\\-3.37}$ & 34.190 \\
ID10 & $9.88\substack{+2.19\\-1.79}$  & $50294.8\substack{+11135.4\\-9116.9}$  & $4.65\substack{+1.03\\-0.84}$ & 9.608 \\
... & $...$ & ... & ... & ...\\
ID991 & $7.90\substack{+1.75\\-1.43}$  & $10175.7\substack{+2252.9\\-1844.5}$  & $7.31\substack{+1.62\\-1.32}$ & 9.354 \\
ID992 & $15.48\substack{+3.43\\-2.81}$  & $8058.1\substack{+1784.1\\-1460.7}$  & $17.14\substack{+3.80\\-3.11}$ & 11.149 \\
ID993 & $6.11\substack{+1.35\\-1.11}$  & $9566.9\substack{+2118.1\\-1734.2}$  & $4.11\substack{+0.91\\-0.75}$ & 10.703 \\
ID994 & $17.41\substack{+3.85\\-3.16}$  & $232095.1\substack{+51386.5\\-42071.7}$  & $14.46\substack{+3.20\\-2.62}$ & 8.444 \\
ID995 & $23.76\substack{+5.26\\-4.31}$  & $127615.4\substack{+28254.4\\-23132.7}$  & $16.97\substack{+3.76\\-3.08}$ & 14.972 \\
ID996 & $10.43\substack{+2.31\\-1.89}$  & $65546.6\substack{+14512.2\\-11881.6}$  & $6.96\substack{+1.54\\-1.26}$ & 9.497 \\
ID997 & $5.79\substack{+1.28\\-1.05}$  & $24315.0\substack{+5383.4\\-4407.6}$  & $6.93\substack{+1.53\\-1.26}$ & 14.177 \\
ID998 & $12.48\substack{+2.76\\-2.26}$  & $98731.2\substack{+21859.3\\-17896.9}$  & $6.85\substack{+1.52\\-1.24}$ & 13.340 \\
ID999 & $6.95\substack{+1.54\\-1.26}$  & $75187.9\substack{+16646.8\\-13629.2}$  & $3.40\substack{+0.75\\-0.62}$ & 9.437 \\
ID1000 & $6.53\substack{+1.45\\-1.18}$  & $27801.3\substack{+6155.3\\-5039.5}$  & $9.79\substack{+2.17\\-1.77}$ & 8.390 \\
%... & $...$ & ... & ... \\
\enddata
\label{tab_GW_mock_data}
\tablecomments{
A demonstration of a thousand-like GW catalog with properties are adopted to estimate the BHMF.
}
\end{deluxetable}

\vspace{1cm}
\section{Theoretical Framework}  \label{sec_theory}
In this section, we describe the fitting for the parameterized BHMFs. 
In principle, the modeling for a dataset which follows power-law distribution as Equation~\ref{equ_powlaw} is very straightforward. To derive the posterior of the parameters, one only needs to combine all the measured points together and joint the likelihood by:
 \begin{equation} \label{equ_lik_powlaw}
 P(\alpha, M_{max}, M_{min}|m_{1}) \propto  \prod_{i=1}^{total} P(m_{1,i}|\alpha, M_{max}, M_{min}).
 \end{equation}
However, the obtained \mone\ in Table~\ref{tab_GW_mock_data} actually deviate from the initial power-law distribution. This deviation stems from several steps as exist in the realistic. In Section~\ref{sec_likelihood_noise} and \ref{sec_likelihood_sf}, we introduce them and explore the ways to account for.

\subsection{Measurement Uncertainty}\label{sec_likelihood_noise}
The intrinsic \mone\ follows a power-law distribution, however the measured  \mone\ are disturbed by Log-Normal distribution and thus they do not follow a power-law function anymore \citep{Koen2009}. In theory, if event $X$ follows a power-law distribution and is observed subject to the Gaussian error, then $X + e$ is distributed as the convolution of the power-law and Gaussian distributions. Likewise, given that the nosied data follows the Log-Normal distribution, the intrinsic power-law should be convolved in the likelihood as:
 \begin{equation} \label{equ_lik_conv}
 P(\alpha, M_{max}, M_{min}) \propto  \prod_{i=1}^{total} \hat{P}(m_{1,i}|\alpha, M_{max}, M_{min}),
 \end{equation}
where the $\hat{P}$ is the convolved power-law function convolved with the Log-Normal distribution using the standard deviation as 0.2 as we assumed. We illustrate the effect of such convolving in this Figure~\ref{fig:result_slope}.
